hbm_paper_results

### 2024-05-01 paper_lbcc_results.Rmd
cleaning up, demographics

@@

>>>>

Number of models converged in each dataset
```{r}
length(raw.feat_to_test)
length(gam.feat_to_test)
length(gamlss.feat_to_test)

#missing features
c(setdiff(pheno_list, gamlss.feat_to_test),
setdiff(pheno_list, raw.feat_to_test),
setdiff(pheno_list, gam.feat_to_test)) %>% unique()
```

```{r}
summary(lm(mean_cent ~ study, data=gamlss_centile_df.mean))
summary(lm(mean_cent ~ study, data=gam_centile_df.mean))
summary(lm(mean_cent ~ study, data=raw_centile_df.mean))
```

@@

feat_aov.df %>%
  group_by(combat) %>%
  summarize(n_sig = sum(sig_fdr))
